How do we get from object recognition\\ to object naming?

### 2018-07-09 papers/SiVL2018/objectnaming.tex
adds label

\section{Requirements}
In order to study object naming as prompted by real-world images, not only do we need to collect names naturally generated by speakers, but also to quantify those factors whose interaction with naming we want to analyze. As we saw, phenomena that impacts on object naming are both perceptual and linguistic in nature: since we here focus on perception as vision, we distinguish between those that pertain language, vision or both.

>>>>

\section{Requirements}
\label{sec:requirements}
In order to study object naming as prompted by real-world images, not only do we need to collect names naturally generated by speakers, but also to quantify those factors whose interaction with naming we want to analyze. As we saw, phenomena that impacts on object naming are both perceptual and linguistic in nature: since we here focus on perception as vision, we distinguish between those that pertain language, vision or both.
